% Example grading policy
Grades will be based on several aspects. The project, worth 35\% of your grade, will involve pitching an idea, designing and presenting your design, and then implementing and programming your project.
You will work with a team of 2 to 4 other students.
This grade will be determined in part by my evaluation of the project and in part by your team members' evaluation of your contribution.
Periodic presentations and written reports, reporting on peers and progress, will account for 60\% of your grade.

The Participation, Effort and Contributions grade will be determined in part by my evaluation of your contributions, your class participation and in part by your team members’ evaluation of your contributions.
Your final project grade is determined by the following calcuation: $(\mathcal{A}/5.0) * (\mathcal{P})$, where $\mathcal{A}$ is your Participation, Effort and Contributions grade (out of 5 points),
and $\mathcal{P}$ is your group project grade.

\textbf{You must receive a grade of (50/100) on your individual project grade to pass this course.}
Listed below is the complete breakdown:
\par\vspace{1cm}
% Grading Breakdown
\begin{tabular}{ @{}ll@{} }
    \toprule
        Area & Percentage \\
    \midrule
        Project: & 35\% \\
        Major Presentations (Expect 2): & 25\% \\
        Weekly Presentations: & 25\% \\
        Participation, Effort and Contributions: & 5\% \\
        Periodic Peer Reports: & 10\% \\
        Total: & 100\% \\
    \bottomrule
\end{tabular}